Meta-analysis Manuscript Wrangling

### 2021-07-05 shared analysis files /manuscript_datavis_22jun21.Rmd
figuring out plots of model results

```{r, echo=FALSE, results = 'hide', message=FALSE}
## loading libraries 
pacman::p_load(metafor, tidyverse, viridis, visreg, forcats)

#load data
dat_acclim_0<- read_csv("acclimation_dummytherm_30jun.csv")
dat_full_var_0 <- read_csv("metafor.csv")
```

@@

## Acclimation without modifiers
```{r, echo=FALSE, message=FALSE}
simple_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, 
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
simple_acclimation_model
```

## Acclimation with modifiers
```{r, echo=FALSE, message=FALSE}
acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
acclimation_model
```

# Acclimation data split out by CT data and other thermal performance metrics 
```{r, echo=FALSE, message=FALSE}
CT_acclim_data <- dat_acclim_ES %>%
  filter(resp_def %in% c("CTmax", "CT max", "CTmin", "LTmax", "LTmin", "Topt", "Tpref", "Thermal preference", "ULT50", "Scope of thermal tolerance (CTmax - CTmin)"))

@@

## CT aggregated model 
```{r, echo=FALSE, message=FALSE}
CT_model <-rma.mv(yi, vi, data=CT_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
CT_model
```
## Remaining acclimation metrics model 
```{r, echo=FALSE, message=FALSE}
curve_model <- rma.mv(yi, vi, data=curve_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
curve_model
```

## Non-linear averaging model with no modifiers
```{r, echo= FALSE, message=FALSE}
simple_full_var_model <- rma.mv(yi, vi, data=dat_full_var_ES, 
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
simple_full_var_model
```

## Non-linear averaging model with modifiers
```{r, echo = FALSE, message=FALSE}
full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, mods = ~flux_range * mean_temp_constant +
                        exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_var_model
```

# Figures
```{r, echo = FALSE, message=FALSE}
dat_acclim_ES %>%
  filter(yi > -5) %>%
ggplot(aes(x=mean_temp_reared, y = yi, fill=flux_range))+
  geom_point(alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Temperature range (°C)', option = "C")+
  theme_classic()+
  xlab("Mean Temperature (°C)")+
  ylab("SMD")+
  geom_line(y=0, linetype = "dashed")+
  theme(legend.position="bottom")+
  ggtitle("Acclimation")
```

```{r, echo = FALSE, message=FALSE}
dat_full_var_ES %>%
  filter(yi > -5) %>%
ggplot(aes(x=mean_temp_constant, y = yi, fill=flux_range))+
  geom_point(alpha = 0.9, pch=21,size=3,colour="black", width = 0.7, height = 0.7)+
  scale_fill_viridis('Temperature range (°C)', option = "C")+
  theme_classic()+
  xlab("Mean Temperature (°C)")+
  ylab("SMD")+
  geom_line(y=0, linetype = "dashed")+
  theme(legend.position="bottom")+
  ggtitle("Non-linear averaging")
```

>>>>

```{r, echo=FALSE, results = 'hide', message=FALSE}
## loading libraries 
pacman::p_load(metafor, tidyverse, viridis, visreg, forcats, devtools, patchwork, R.rsp)
#devtools::install_github("itchyshin/orchard_plot", subdir = "orchaRd", method= 'libcurl', force = TRUE, build_vignettes = TRUE)
library(orchaRd)
#load data
dat_acclim_0<- read_csv("acclimation_dummytherm_30jun.csv")
dat_full_var_0 <- read_csv("metafor.csv")
```

@@

## Acclimation with temperature modifiers
```{r, echo=FALSE}
temp_acclimation_model <- rma.mv(yi, vi, data=dat_acclim_ES, mods=~flux_range * mean_temp_reared,
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
temp_acclimation_model
```

## Acclimation with trait modifiers
```{r, echo=FALSE}
trait_acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, 
                                mods = ~exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
trait_acclimation_model
```

## Acclimation with all modifiers
```{r, echo=FALSE}
acclimation_model<-rma.mv(yi, vi, data=dat_acclim_ES, 
            mods = ~flux_range * mean_temp_reared + exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
acclimation_model
```

## Non-linear averaging model with temperature modifiers
```{r, echo= FALSE}
temp_full_var_model <- rma.mv(yi, vi, data=dat_full_var_ES, 
                                mods = ~flux_range * mean_temp_constant,
               random = ~1 | study_id / experiment_id/ response_id,
                 method="REML") 
temp_full_var_model
```

## Non-linear averaging model with trait modifiers
```{r, echo = FALSE}
trait_full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, mods = ~exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
trait_full_var_model
```

## Non-linear averaging model with all modifiers
```{r, echo = FALSE}
full_var_model <-rma.mv(yi, vi, data=dat_full_var_ES, 
                        mods = ~flux_range * mean_temp_constant + exp_age + size + org_level, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML") 
full_var_model
```

```{r}
#Model selection 
AIC(temp_acclimation_model, trait_acclimation_model, acclimation_model, temp_full_var_model, trait_full_var_model, full_var_model)
```

# Figures

```{r, echo=FALSE}
normalized_acclim <- dat_acclim_ES %>% filter(between(yi, -5, 5))
normalized_var <- dat_full_var_ES  %>% filter(between(yi, -5, 5))

dummy_acclim <- rma.mv(yi, vi, data=normalized_acclim, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
dummy_var <- rma.mv(yi, vi, data=normalized_var, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")

I2_acclim <- i2_ml(dummy_var)
I2_var <-i2_ml(dummy_acclim)

p1 <- orchard_plot(dummy_acclim, mod = "Int", xlab = "Standardised mean difference", transfm = "none", )+
  annotate(geom = "text", x = 0, y = 1.5, label = "Acclimation")+
  annotate(geom = "text", x = -4.7, y = 1.5, label = paste0("italic(I)^{2} == ",
round(I2_acclim[1] * 100, 2)), color = "black", parse = TRUE, size = 5) + annotate(geom = "text",
x = -3.7, y = 1.49, label = "%", color = "black", parse = FALSE, size = 5)

p2 <- orchard_plot(dummy_var, mod = "Int", xlab = "Standardised mean difference", transfm = "none")+
  annotate(geom = "text", x = 0, y = 1.5, label = "Non-linear averaging and acclimation")+
  annotate(geom = "text", x = -4.1, y = 1.5, label = paste0("italic(I)^{2} == ",
round(I2_var[1] * 100, 2)), color = "black", parse = TRUE, size = 5) + annotate(geom = "text",
x = -3.1, y = 1.49, label = "%", color = "black", parse = FALSE, size = 5)
p1 / p2
```

```{r, echo=FALSE}
forest_acclim<- dat_acclim_ES %>%
  group_by(mean_temp_reared, flux_range) %>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  unite(group, c(mean_temp_reared, flux_range), sep = " range ", remove = FALSE)%>%
  arrange(desc(flux_range))

forest_var<- normalized_var %>%
  group_by(mean_temp_constant, flux_range) %>%
  summarise(mean_yi = mean(yi),
            mean_vi = mean(vi)) %>%
  unite(group, c(mean_temp_constant, flux_range), sep = "+/-", remove = FALSE) %>%
  arrange(desc(flux_range))

forest(forest_acclim$mean_yi, forest_acclim$mean_vi, slab=forest_acclim$group, pch =19, psize=1, col = "gray2", 
       header=TRUE, cex=0.77)

forest(forest_var$mean_yi, forest_var$mean_vi, slab=forest_var$group, pch =19, psize=1, col = "gray2", 
       header=TRUE, cex=0.77)

```

## Funnel plot of acclimation data 
````{r, echo=FALSE}
funnel(dummy_acclim, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), refline=0, legend=TRUE)
```
## Funnel plot of non-linear averaging + acclimation data 
````{r, echo=FALSE}
funnel(dummy_var, level=c(90, 95, 99), shade=c("white", "gray55", "gray75"), refline=0, legend=TRUE)
```

```{r, echo=FALSE}
p3<-normalized_acclim %>%
  ggplot(aes(x=flux_range, y=yi, color=as.factor(mean_temp_reared)))+
  scale_color_viridis(discrete=TRUE)+
  geom_point(size=3, alpha =0.5)+
  geom_smooth(method="lm")+
  theme_bw()

p4<-normalized_var %>%
  ggplot(aes(x=flux_range, y=yi, color=as.factor(mean_temp_constant)))+
  scale_color_viridis(discrete=TRUE)+
  geom_point(size= 3, alpha =0.5)+
  geom_smooth(method="lm")+
  theme_bw()
p3/p4

normalized_acclim %>%
  ggplot(aes(x=as.factor(flux_range), y=yi, color=as.factor(mean_temp_reared)))+
  scale_color_viridis(discrete = TRUE)+
  geom_boxplot()+
  geom_point(alpha=0.5)+
  theme_bw()

normalized_var %>%
  ggplot(aes(x=as.factor(flux_range), y=yi, color=as.factor(mean_temp_constant)))+
  scale_color_viridis(discrete = TRUE)+
  geom_boxplot()+
  geom_point(alpha=0.5)+
  theme_bw()

```

# Supplementary code and models

## Acclimation data split out by CT data and other thermal performance metrics 
```{r, echo=FALSE, message=FALSE, results='hide'}
CT_acclim_data <- dat_acclim_ES %>%
  filter(resp_def %in% c("CTmax", "CT max", "CTmin", "LTmax", "LTmin", "Topt", "Tpref", "Thermal preference", "ULT50", "Scope of thermal tolerance (CTmax - CTmin)"))

@@

## CT aggregated model 
```{r, echo=FALSE, message=FALSE, results='hide'}
CT_model <-rma.mv(yi, vi, data=CT_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
CT_model
```
## Remaining acclimation metrics model 
```{r, echo=FALSE, message=FALSE, results='hide'}
curve_model <- rma.mv(yi, vi, data=curve_acclim_data, mods = ~flux_range * mean_temp_reared +
                        exp_age + size + org_level + exposure_temp, 
               random = ~1 |  study_id/ experiment_id/ response_id,
                 method="REML")
curve_model
```
